Differential Expression

### 2020-04-05 cmc-rnaseq-de/Differential-Expression.Rmd
remove missing factor covariates for this cohort

# Set variable class
FactorCovariates <- c("Individual_ID", "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "RibozeroBatch", "FlowcellBatch")
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)

>>>>

# Set variable class
FactorCovariates <- c("Individual_ID", "Reported_Gender", "Dx.Tissue")
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
